Binning Strategies and Related Loss for Large Data

### 2015-04-26 Paper.Rnw
minor grammar edits

\item {\it Frequency Loss}, $L^\text{F}$, occurs when bin counts, $c_\ell \in \{1,\dots,\mathscr{L}\}$ are not rendered precisely. A discrete color scale may be used to aid the ability to read a binned scatterplot, however this is effectively a second stage of binning where shade displays binned frequencies, $b_C(c_\ell)$ for bins $\ell \in \{1,\dots,\mathscr{L}\}$, thus losing precision in the display of the true frequencies. This is analogous to the fundamental problem for over-plotted standard scatterplots where frequency is masked by other points. 
\end{itemize}
}

>>>>

\item {\it Frequency Loss}, $L^\text{F}$, occurs when bin counts, $c_\ell \in \{1,\dots,\mathscr{L}\}$ are not rendered precisely. A discrete color scale may be used to aid the ability to read a binned scatterplot, however this is effectively a second stage of binning where shade displays binned frequencies, $b_C(c_\ell)$, for spatial bins $\ell \in \{1,\dots,\mathscr{L}\}$, thus losing precision in the display of the true frequencies. This is analogous to the fundamental problem for over-plotted standard scatterplots where frequency is masked by other points. 
\end{itemize}
}
